---
title: "Homework 1"
output:
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: xelatex
---
```{r setup, message = F, include=FALSE}
options(htmltools.dir.verssion = FALSE)
suppressWarnings(expr)
library(tidyverse)
library(DAAG)
library(installr)
install.Rtools()
```

1. The Iowa data set iowa.csv is a toy example that summarises the yield of wheat (bushels per acre) for the state of Iowa between 1930-1962. In addition to yield, year, rainfall and temperature were recorded as the main predictors of yield.
    a. First, we need to load the data set into R using the command `read.csv()`. Use the help function to learn what arguments this function takes. Once you have the necessary input, load the data set into R and make it a data frame called `iowa.df`.
    b. How many rows and columns does `iowa.df` have? 
    c. What are the names of the columns of `iowa.df`?
    d. What is the value of row 5, column 7 of `iowa.df`?
    e. Display the second row of `iowa.df` in its entirety.
```{r message=FALSE, warning=FALSE}
iowa.df<-read.csv("data/iowa.csv",header=T,sep=";")  
nrow(iowa.df)  
ncol(iowa.df)  
rownames(iowa.df)  
colnames(iowa.df)  
iowa.df[5,7]  
iowa.df[2,]  
```

2. Syntax and class-typing.
    a. For each of the following commands, either explain why they should be errors, or explain the non-erroneous result.

```
vector1 <- c("5", "12", "7", "32")  
max(vector1)  
sort(vector1)  
sum(vector1)  
#d<e:igf/sum,e d8:h>e%g"5","12","7","32"f/"character"gf <e<
```
    b. For the next series of commands, either explain their results, or why they should produce errors.

```
vector2 <- c("5",7,12)
#vector2[2] + vector2[3]
#h?d8