---
title: 'Homework 2: Housing Price'
output:
  html_document:
    df_print: paged
---
```{r setup,  include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(DAAG)
library(MASS)
library(conflicted)
conflict_prefer("select","dplyr")
conflict_prefer("filter","dplyr")
#the result return the number of the no value in the dataframe.
```
1. _Loading and cleaning_
    a. Load the data into a dataframe called `ca_pa`.
```{r}
ca_pa<-read.csv("data/calif_penn_2011.csv")
```
    b. How many rows and columns does the dataframe have?
```{r}
ncol(ca_pa)
nrow(ca_pa)
```
    c. Run this command, and explain, in words, what this does:
```
colSums(apply(ca_pa,c(1,2),is.na))
#it returns the number of cell with "NA" in the data frame.
```
    d. The function `na.omit()` takes a dataframe and returns a new dataframe, omitting any row containing an NA value.  Use it to purge the data set of rows with incomplete data.
```{r}
ca_pa.omit<-na.omit(ca_pa)
```
    e. How many rows did this eliminate?
```{r}
nrow(ca_pa)-nrow(ca_pa.omit)
#670 rows.
```
    f. Are your answers in (c) and (e) compatible? Explain.
    No, because there are more than one NA in some rows.
    
2. _This Very New House_  
    a. The variable `Built_2005_or_later` indicates the percentage of houses in each Census tract built since 2005.  Plot median house prices against this variable.
```{r}
ca_pa.05<-ca_pa$Built_2005_or_later
ca_pa.me<-ca_pa$ Median_house_value
plot(ca_pa.me,ca_pa.05,xlab = "Built_2005_or_later",ylab = "median house prices")
```
    b. Make a new plot, or pair of plots, which breaks this out by state.  Note that the state is recorded in the `STATEFP` variable, with California being state 6 and Pennsylvania state 42.
```{r}
ggplot(data = ca_pa) +
    geom_point(aes(x =Median_house_value, y = Built_2005_or_later, color = STATEFP))+
    facet_wrap(~ STATEFP)
```
    

3. _Nobody Home_  
The vacancy rate is the fraction of housing units which are not occupied.  The dataframe contains columns giving the total number of housing units for each Census tract, and the number of vacant housing units.  
    a. Add a new column to the dataframe which contains the vacancy rate.  What are the minimum, maximum, mean, and median vacancy rates?
```{r}
ca_pa.new <- mutate(ca_pa,the_vacancy_rate = Vacant_units / Total_units)
```
    b. Plot the vacancy rate against median house value.
```{r}
ggplot(data = ca_pa.new) +
    geom_point(aes(x =Median_house_value, y = the_vacancy_rate))
```
    
    c. Plot vacancy rate against median house value separately for California and for Pennsylvania.  Is there a difference?
```{r}
ggplot(data = ca_pa.new)+
  geom_point(aes(x = Median_house_value, y = the_vacancy_rate,color = STATEFP)) +
  facet_wrap(~ STATEFP)
```

    
4. The column `COUNTYFP` contains a numerical code for counties within each state.  We are interested in Alameda County (county 1 in California), Santa Clara (county 85 in California), and Allegheny County (county 3 in Pennsylvania).
    a. Explain what the block of code at the end of this question is supposed to accomplish, and how it does it.
```
acca <- c()
for (tract in 1:nrow(ca_pa)) {
  if (ca_pa$STATEFP[tract] == 6) {
    if (ca_pa$COUNTYFP[tract] == 1) {
      acca <- c(acca, tract)
    }
  }
}
accamhv <- c()
for (tract in acca) {
  accamhv <- c(accamhv, ca_pa[tract,10])
}
median(accamhv)

#this code sifts all the stata of house value related to Alameda County, and then calculate the median number.
    
```
    b. Give a single line of R which gives the same final answer as the block of code.  Note: there are at least two ways to do this; you just have to find one.
```{r}
median((na.omit(ca_pa)%>%filter(COUNTYFP==1,STATEFP==6))$Median_house_value)
```
    c. For Alameda, Santa Clara and Allegheny Counties, what were the average percentages of housing built since 2005?
```{r}
#Alameda 
ca_pa.ala1<-filter(ca_pa.omit,COUNTYFP==1,STATEFP==6)$Built_2005_or_later
ca_pa.ala2<-filter(ca_pa.omit,COUNTYFP==1,STATEFP==6)$Total_units
ca_pa.ala<-ca_pa.ala1/ca_pa.ala2
sum(ca_pa.ala1/ca_pa.ala2)*100
#Santa Clara
ca_pa.sc1<-filter(ca_pa.omit,COUNTYFP==85,STATEFP==6)$Built_2005_or_later
ca_pa.sc2<-filter(ca_pa.omit,COUNTYFP==85,STATEFP==6)$Total_units
sum(ca_pa.sc1/ca_pa.sc2)*100
#Allegheny Counties
ca_pa.all1<-filter(ca_pa.omit,COUNTYFP==3,STATEFP==42)$Built_2005_or_later
ca_pa.all2<-filter(ca_pa.omit,COUNTYFP==3,STATEFP==42)$Total_units
ca_pa.all<-ca_pa.all1/ca_pa.all2
sum(ca_pa.all1/ca_pa.all2)*100
```
    d. The `cor` function calculates the correlation coefficient between two variables.  What is the correlation between median house value and the percent of housing built since 2005 in (i) the whole data, (ii) all of California, (iii) all of Pennsylvania, (iv) Alameda County, (v) Santa Clara County and (vi) Allegheny County?
```{r}
#the whole data
cor(ca_pa.omit$Median_house_value,ca_pa.omit$Built_2005_or_later)

##Alameda 
ca_pa.ala1<-filter(ca_pa.omit,COUNTYFP==1,STATEFP==6)$Built_2005_or_later
ca_pa.ala2<-filter(ca_pa.omit,COUNTYFP==1,STATEFP==6)$Median_house_value
cor(ca_pa.ala1,ca_pa.ala2)

#Santa Clara
ca_pa.sc1<-filter(ca_pa.omit,COUNTYFP==85,STATEFP==6)$Built_2005_or_later
ca_pa.sc2<-filter(ca_pa.omit,COUNTYFP==85,STATEFP==6)$Median_house_value
cor(ca_pa.sc1,ca_pa.sc2)

#Allegheny Counties
ca_pa.all1<-filter(ca_pa.omit,COUNTYFP==3,STATEFP==42)$Built_2005_or_later
ca_pa.all2<-filter(ca_pa.omit,COUNTYFP==3,STATEFP==42)$Median_house_value
cor(ca_pa.all1,ca_pa.all2)
```
    e. Make three plots, showing median house values against median income, for Alameda, Santa Clara, and Allegheny Counties.  (If you can fit the information into one plot, clearly distinguishing the three counties, that's OK too.)
```{r}
ggplot(data = (ca_pa.omit %>%
filter(COUNTYFP==1,STATEFP==6) %>%     select(COUNTYFP,Median_house_value,Median_household_income))) +
  geom_point(aes(x = Median_house_value, y = Median_household_income))

ggplot(data = na.omit(ca_pa %>% filter(COUNTYFP==85,STATEFP==6) %>%     select(Median_house_value,Median_household_income))) +
  geom_point(aes(x = Median_house_value, y = Median_household_income))

ggplot(data = na.omit(ca_pa %>% filter(COUNTYFP==3,STATEFP==42) %>%     select(Median_house_value,Median_household_income))) +
  geom_point(aes(x = Median_house_value, y = Median_household_income))
```


MB.Ch1.11. Run the following code:
```
gender <- factor(c(rep("female", 91), rep("male", 92)))
table(gender)
gender <- factor(gender, levels=c("male", "female"))
table(gender)
gender <- factor(gender, levels=c("Male", "female"))
# Note the mistake: "Male" should be "male"
table(gender)
table(gender, exclude=NULL)
rm(gender)  # Remove gender
```
Explain the output from the successive uses of table().

#for the first time, it created "gender" with 92 "female" and 92 "male", and then in the second time, with the use of level(), it changed the location of two columns, after that, in the third time, it replace "male" with "Male". "Male“ has not been assigned, so it's the defaulting number 0, however, the number of male did not eleminate, so when include "null", wen can still see a number"92". 

MB.Ch1.18. The Rabbit data frame in the MASS library contains blood pressure change measurements on five rabbits (labeled as R1, R2, . . . ,R5) under various control and treatment conditions. Read the help file for more information. Use the unstack() function (three times) to convert Rabbit to the following form:

Treatment Dose   R1   R2   R3   R4   R5 

1 Control 6.25  0.50 1.00 0.75 1.25 1.5 

2 Control 12.50 4.50 1.25 3.00 1.50 1.5 

....
```{r}
Rabbit.1<-unstack(Rabbit,BPchange~Animal)
Dose<-unstack(Rabbit, Dose~Animal)[,1]
Treatment<-unstack(Rabbit, Treatment~Animal)[,1]
Rabbit.new<-data.frame(Treatment,Dose,Rabbit.1)
```


